---
title: "Using `namedarray`"
subtitle: "A mini-utility package for setting up a storage system" 
author: "Bruno Fischer Colonimos"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using namedarray}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  # collapse = TRUE,
  comment = "#>"
)
```

If you often end up writing code to store and retrieve options or parameters, this utility might be useful to you

# Storage of options/parameters: an example

**Example**: If we wish to output formatted text in either Latex or Html,
We have to remember that formatting such as  emphasis, strong emphasis and centering (for example) are obtaned with different markup in these languages.

Let us decide that we will define and store "prefix" and "suffix" strings for each of these formatting effects, and each language.

## Setting up the system

We set up the system with the function `setup_nametable`:
```{r}
library(namedarray)
fstr <- setup_nametable(argnames = c("language", 
                                     "effect", 
                                     "position"),
                        argranges = list(c("html", "latex"),
                                         c("emphasis", 
                                           "strong", 
                                           "center"),
                                         c("prefix", "suffix")))
```

This code assigns to `fstr` a named list of 2 functions (`set` and `get`), used respectively to store and to access the values, selecting them with a combination of the three named argument : `language` , `effect` , `position`.

These arguments act as the `dimnames` of an array (and are ideed currently implemented as such) : a missing argument means that all possible values for this argument will be included in the selection.

## Using the generated functions

### Setting up values 

```{r}
# setting the empty string as the default string
fstr$set( , value = "")  # no selector argument specified , ie all values are part or the selection

# setting the prefix and suffix for the centering effect
fstr$set(language = "html", effect = "center", position = "prefix", 
         value = "<center> ")
fstr$set(language = "html", effect = "center", position = "suffix", 
         value = "</center> ")
fstr$set(language = "latex", effect = "center", position = "prefix", 
         value = "\\begin{centering}")
fstr$set(language = "latex", effect = "center", position = "suffix", 
         value = "\\end{centering}")

# Similar code should be set up for the other effects

```

### Retrieving values

```{r}
# get one value
fstr$get(language = "latex", effect = "center", position = "suffix")

# get an array of values
fstr$get(language = "latex") 
```

## Limitations
With the current implementation, all the values should have the same type. 
